MCC Predictions

### 2018-05-02 stats/ex3_comparisons.Rmd
noisy model predictions

    var conditionSpecificData =  _.filter(allData, {Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Experiment: conditionInfo.Experiment})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Experiment: conditionInfo.Experiment})

@@

jsonlite::toJSON(priorProbs, pretty = T)

>>>>

    var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})

@@

jsonlite::toJSON(allConditions, pretty = T)

jsonlite::toJSON(allPriorProbs, pretty = T)
